General constraints on magic distillation protocols from statistical mechanics

### 2021-06-04 magic_paper.tex
expanded on argument why alpha = even/even works

Consider the partial derivatives
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1}).
\end{equation}
Whenever $w_i \geq w_j$, for $\alpha$ in the given form, we always have that $\alpha - 1$ is positive and of the form odd$/$odd so \nick{expand argument}
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which leads to
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
\end{equation}
Therefore, $H_\alpha$ is Schur-concave and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$.

>>>>

Consider the partial derivatives
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} = \frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}}(-w_i^{\alpha-1}).
\end{equation}
We first note that for $\alpha$ in the given form, it is always true that
\begin{equation}
	\frac{\alpha}{(\alpha-1)\sum_k{w_k^\alpha}} > 0.
\end{equation}
We then show that for $\alpha$ in the given form, the function $f(w) = -w^{\alpha - 1}$ is non-increasing.
To this end, we obtain the first derivative
\begin{equation}
	f'(w) = -(\alpha - 1) w^{\alpha-2} = -(\alpha - 1)w^{\frac{2a-4b+2}{2b-1}} \leq 0,
\end{equation}
because $\alpha > 1$ and
\begin{equation}
	w^{\frac{2a-4b+2}{2b-1}} = \left(w^{2a-4b+2}\right)^{\frac{1}{2b-1}} = \left(w^{\frac{1}{2b-1}}\right)^{2(a-2b+1)} \geq 0,
\end{equation}
where each expression is well defined because the rational exponent has even numerator and odd denominator.
\nick{This step is the reason why $\alpha =$ odd$/$odd or $\alpha < 1$ do not work. $\alpha - 2$ may be less than 0, is this a problem?}

Therefore, whenever $w_i \geq w_j$, we have that 
\begin{equation}
	-w_i^{\alpha-1} \leq -w_j^{\alpha-1},
\end{equation}
which leads to
\begin{equation}
	\frac{\partial H_\alpha}{\partial w_i} \leq \frac{\partial H_\alpha}{\partial w_j}.
\end{equation}
Therefore, $H_\alpha$ is Schur-concave and
\begin{equation}
	H_\alpha(\w) \leq H_\alpha(\w'),
\end{equation}
for any quasi-distributions $\w, \w'$.
